### 2016-08-09 main.tex
Replace fig:accuracies (Fig. 3) with the new one that includes test results for cage noise.  Add a table for syllable-by-syllable variation in accuracies.

\begin{abstract}
  The song of the adult male zebra finch is strikingly stereotyped.
  Efforts to understand motor output, pattern generation, and learning
  have taken advantage of this consistency by investigating the bird's
  ability to modify specific parts of song under external cues, and by
  examining timing relationships between neural activity and vocal
  output.  Such experiments require that precise moments during song
  be identified in real time as the bird sings.  Various
  syllable-detection methods exist, but many require special hardware,
  software, and know-how, and details on their implementation and
  performance are scarce.  We present an accurate, versatile, and fast
  syllable detector that can control hardware at precisely timed
  moments during zebra finch song.  Many moments during song can be
  isolated and detected with false negative and false positive rates
  well under 0.5\% and 0.01\% respectively. The detector can run on a
  stock Mac Mini with triggering delay of less than a millisecond and
  a jitter of $\sigma\approx 2$ milliseconds.
\end{abstract}

@@

\begin{enumerate}
\item Record and align a corpus of training songs.  The technique has been published in \cite{Poole2012}.
\item Choose one or more instants in the song that should create a trigger event, and train a
  neural network to recognise them. This step is carried out offline.  While any neural network software would produce equivalent results, we used MATLAB 2015b's neural network toolbox.
\item Once trained and saved, the neural network is used by a realtime
  detection program that listens to an audio signal and indicates detection of the target
  syllables via a TTL pulse.  We present three implementations, in MATLAB, LabVIEW, and Swift, that trade off hardware requirements, ease of maintenance, and performance.
\end{enumerate}
This method makes the following contributions:
\begin{itemize}
\item Fast: sub-millisecond latencies, with jitter around 2 ms.
\item Accurate: false positive rates under 0.02\% and false negative rates under 0.5\% for a variety of syllables.  Balancing these rates depends on a single relative-cost parameter.
\item State-of-the-art performance with default parameters.
\item Runs on inexpensive hardware.
\item Described in detail here, with reference implementations provided and benchmarked.
\end{itemize}

@@

\begin{figure}
  \includegraphics[width=\textwidth]{Fig2}
  % 9x10 inches
  % Fonts: Helvetica, scaled 130%
  \caption{Each plot shows one network output unit's responses to all
    2818 presentations of the song shown in \fig{fig:song}.  For
    simplicity, we show only the syllables $t^*_1$, $t^*_4$, and
    $t^*_6$. The horizontal axis is time relative to the beginning of
    the aligned song, and the vertical axis is an index for the 2818
    individual song presentations. The grey shading shows the audio
    amplitude of song Y at time T. Detection events on training songs
    are shown in cyan, with detections of unseen test songs in red.  To provide an intuition of intra-song variability, songs have been
    stably sorted by the time of detection events; thus, each of the
    three detection graphs shows the songs in a different order.}
  \label{fig:detection_raster}
\end{figure}

@@

We allowed our training software to allocate our default of 4 hidden
units per syllable, and computed a new FFT every 1.5 ms.  Because our
timing test files are designed for our stereo playback software,
allowing only one channel for the ground-truth pulse, we trained one
detector for each syllable for the following results.  In order to
eliminate the large number of variables involved in microphone, cage,
playback and re-digitising, we evaluated the neural network's accuracy
directly on the digitised recording.  When training and runtime data
are gathered on the same hardware setup, this is the digital signal
that the detector will see---only the non-song data may be different.
%Accuracy \marginpar{Should be! Verify! And/or explain that there is a bug in the LabVIEW implementation, if there in fact is. ALSO need to present a picture of the test syllable or etc\dots} is identical across the three detectors.
\noprint{
  Typical confusion matrices for these syllables are:

  \vspace{8pt}\par\noindent
  \begin{tabular}{r|cc}
    $t^*_1$
    & \multicolumn{2}{c}{True} \\ 
    & pos & neg \\ 
    \hline  Detected pos & 99.96451\% & 0.000298\%\\ 
    neg & 0.0355\% & 99.99970\%\\ 
  \end{tabular}
  \vspace{8pt}\par\noindent
  \begin{tabular}{r|cc}
    $t^*_2$ & \multicolumn{2}{c}{True} \\ 
    & pos & neg \\ 
    \hline  Detected pos & 99.92903\% & 0.000596\%\\ 
    neg & 0.0710\% & 99.99940\%\\ 
  \end{tabular}
  \vspace{8pt}\par\noindent
  \begin{tabular}{r|cc}
    $t^*_3$ & \multicolumn{2}{c}{True} \\ 
    & pos & neg \\ 
    \hline  Detected pos & 99.68062\% & 0.00194\%\\ 
    neg & 0.319\% & 99.99806\%\\ 
  \end{tabular}
  \vspace{8pt}\par\noindent
  \begin{tabular}{r|cc}
    $t^*_4$ & \multicolumn{2}{c}{True} \\ 
    & pos & neg \\ 
    \hline  Detected pos & 99.82257\% & 0.00239\%\\ 
    neg & 0.177\% & 99.99761\%\\ 
  \end{tabular}
  \vspace{8pt}\par\noindent
  \begin{tabular}{r|cc}
    $t^*_5$ & \multicolumn{2}{c}{True} \\ 
    & pos & neg \\ 
    \hline  Detected pos & 99.78708\% & 0\\ 
    neg & 0.213\% & 100\%\\ 
  \end{tabular}
  \vspace{8pt}\par\noindent
  \begin{tabular}{r|cc}
    $t^*_6$ & \multicolumn{2}{c}{True} \\ 
    & pos & neg \\ 
    \hline  Detected pos & 99.71611\% & 0.00552\%\\ 
    neg & 0.284\% & 99.99448\%\\ 
  \end{tabular}
  \vspace{8pt}\par\noindent
}

Accuracies for our six test syllables are shown in
\fig{fig:accuracies} (accuracies for the synthetic $\delta$-function
songs were always 100\%).  For each test syllable we trained
100 different
networks, which differ from each other in the random initialisation of
network weights and on which random subset of our songs was used for
training.  Each network's accuracy is shown as a single point in each
chart in \fig{fig:accuracies}.  Some syllables are easier to identify
reliably than others, allowing detection point choice to impact the
detector's accuracy.  For difficult syllables, the training process
occasionally yields a network that performs unusually poorly, but it
is easy to spot these networks by their performance either as measured
as part of the training process or on the test audio file, and
re-train when necessary.

@@

  \caption{Accuracy variability over 100 different training runs for each
    of the six test syllables.  Each dot shows the test-set accuracy
    for an independently trained detector.  Because the horizontal
    positions have been randomised slightly so as not to occlude same-valued
    measurements, test syllable is also indicated by colour.}
  \label{fig:accuracies}
\end{figure}

@@

This syllable detector is appropriate for zebra finch song, and
although our tests were carried out on songs from that species, it is
also likely to work well for Bengalese finches due to their similarly stereotyped syllables.  It offers the
following benefits:
\begin{itemize}
\item The detector is accurate. False negative and false positive
  rates can be well under 0.5\% and 0.01\% respectively, and trading
  these two numbers off against each other is through a single
  relative-cost parameter.
\item Latency is generally under a millisecond, with jitter around 2
  ms.
\item Works on a wide range of target syllables using the default
  values described here, generally eliminating the need for
  hand-tuning.
\item Runs fast enough for syllable-modification experiments on
  inexpensive consumer-grade hardware, although we recommend that the
  training phase be run on a fast desktop system with 32 GB of RAM.
\item A single detector can generate different target pulses for
  multiple syllables at almost no additional computational cost during
  runtime, although training time will increase.
\end{itemize}

>>>>

\begin{abstract}
  The song of the adult male zebra finch is strikingly stereotyped.
  Efforts to understand motor output, pattern generation, and learning
  have taken advantage of this consistency by investigating the bird's
  ability to modify specific parts of song under external cues, and by
  examining timing relationships between neural activity and vocal
  output.  Such experiments require that precise moments during song
  be identified in real time as the bird sings.  Various
  syllable-detection methods exist, but many require special hardware,
  software, and know-how, and details on their implementation and
  performance are scarce.  We present an accurate, versatile, and fast
  syllable detector that can control hardware at precisely timed
  moments during zebra finch song.  Many moments during song can be
  isolated and detected with false negative and false positive rates
  well under 1\% and 0.001\% respectively. The detector can run on a
  stock Mac Mini with triggering delay of less than a millisecond and
  a jitter of $\sigma\approx 2$ milliseconds.
\end{abstract}

@@

\begin{enumerate}
\item Record and align a corpus of training songs.  The technique has been published in \cite{Poole2012}.
\item Choose one or more instants in the song that should create a trigger event, and train a
  neural network to recognise them. This step is carried out offline.  While any neural network software would produce equivalent results, we used MATLAB 2015b's neural network toolbox.
\item Once trained and saved, the neural network is used by a realtime
  detection program that listens to an audio signal and indicates detection of the target
  syllables via a TTL pulse.  We present three implementations, in MATLAB, LabVIEW, and Swift, that trade off hardware requirements, ease of maintenance, and performance.
\end{enumerate}
This method makes the following contributions:
\begin{itemize}
\item Fast: sub-millisecond latencies, with jitter around 2 ms.
\item Accurate: false positive rates under 0.001\% and false negative rates under 1\% for a variety of syllables.  Balancing these rates depends on a single relative-cost parameter.
\item State-of-the-art performance with default parameters.
\item Runs on inexpensive hardware.
\item Described in detail here, with reference implementations provided and benchmarked.
\end{itemize}

@@

\begin{figure}
  \includegraphics[width=\textwidth]{Fig2}
  % 9x10 inches
  % Fonts: Helvetica, scaled 130%
  \caption{Each plot shows one network output unit's responses to all
    2818 presentations of the song shown in \fig{fig:song}.  For
    simplicity, we show only the syllables $t^*_1$, $t^*_4$, and
    $t^*_6$, and we do not show the non-response to presentation of non-song. The horizontal axis is time relative to the beginning of
    the aligned song, and the vertical axis is an index for the 2818
    individual song presentations. The grey shading shows the audio
    amplitude of song Y at time T. Detection events on training songs
    are shown in cyan, with detections of unseen test songs in red.  To provide an intuition of intra-song variability, songs have been
    stably sorted by the time of detection events; thus, each of the
    three detection graphs shows the songs in a different order.}
  \label{fig:detection_raster}
\end{figure}

@@

We allowed our training software to allocate our default of 4 hidden
units per syllable, and computed a new FFT every 1.5 ms.  Because our
timing test files are designed for our stereo playback software,
allowing only one channel for the ground-truth pulse, we trained one
detector for each syllable for the following results.  In order to
eliminate the large number of variables involved in microphone, cage,
playback and re-digitising, we evaluated the neural network's accuracy
directly on the digitised recording.  When training and runtime data
are gathered on the same hardware setup, this is the digital signal
that the detector will see---only the non-song data may be different.
%Accuracy \marginpar{Should be! Verify! And/or explain that there is a bug in the LabVIEW implementation, if there in fact is. ALSO need to present a picture of the test syllable or etc\dots} is identical across the three detectors.

\noprint{
  The means of the false positive and

  \vspace{8pt}\par\noindent
  \begin{tabular}{r|cc}
    $t^*_1$
    & \multicolumn{2}{c}{True} \\ 
    & pos & neg \\ 
    \hline  Detected pos & 99.34\% & 0.0015\%\\ 
    neg & 0.0355\% & 99.99970\%\\ 
  \end{tabular}
  \vspace{8pt}\par\noindent
  \begin{tabular}{r|cc}
    $t^*_2$ & \multicolumn{2}{c}{True} \\ 
    & pos & neg \\ 
    \hline  Detected pos & 99.92903\% & 0.000596\%\\ 
    neg & 0.0710\% & 99.99940\%\\ 
  \end{tabular}
  \vspace{8pt}\par\noindent
  \begin{tabular}{r|cc}
    $t^*_3$ & \multicolumn{2}{c}{True} \\ 
    & pos & neg \\ 
    \hline  Detected pos & 99.68062\% & 0.00194\%\\ 
    neg & 0.319\% & 99.99806\%\\ 
  \end{tabular}
  \vspace{8pt}\par\noindent
  \begin{tabular}{r|cc}
    $t^*_4$ & \multicolumn{2}{c}{True} \\ 
    & pos & neg \\ 
    \hline  Detected pos & 99.82257\% & 0.00239\%\\ 
    neg & 0.177\% & 99.99761\%\\ 
  \end{tabular}
  \vspace{8pt}\par\noindent
  \begin{tabular}{r|cc}
    $t^*_5$ & \multicolumn{2}{c}{True} \\ 
    & pos & neg \\ 
    \hline  Detected pos & 99.78708\% & 0\\ 
    neg & 0.213\% & 100\%\\ 
  \end{tabular}
  \vspace{8pt}\par\noindent
  \begin{tabular}{r|cc}
    $t^*_6$ & \multicolumn{2}{c}{True} \\ 
    & pos & neg \\ 
    \hline  Detected pos & 99.71611\% & 0.00552\%\\ 
    neg & 0.284\% & 99.99448\%\\ 
  \end{tabular}
  \vspace{8pt}\par\noindent
}

Accuracies for our six test syllables are shown in
\fig{fig:accuracies} (accuracies for the synthetic $\delta$-function
songs were always 100\%).  For each test syllable we trained
100 different
networks, which differ from each other in the random initialisation of
network weights and on which random subset of our songs was used for
training.  Each network's accuracy is shown as a single point in each
chart in \fig{fig:accuracies}, and the means are shown in Table~\ref{table:accuracies}.  Some syllables are easier to identify
reliably than others, showing that detection point choice can impact the
detector's accuracy.  As can be seen from \fig{fig:accuracies}, for difficult syllables, the training process
occasionally yields a network that performs unusually poorly, but it
is easy to spot these networks by their performance either as measured
as part of the training process or on the test audio file, and
re-train when necessary.

@@

  \caption{Accuracy variability over 100 different training runs for
    each of the six test syllables.  Each dot shows the test-set
    accuracy for an independently trained detector.  Because the
    horizontal positions have been randomised slightly so as not to
    occlude same-valued measurements, test syllable is also indicated
    by colour.  The means are given in Table~\ref{table:accuracies}.}
  \label{fig:accuracies}
\end{figure}

\begin{table}
  \begin{tabular}{c|rr}
    Target time & \% True positives & \% False positives \\ \hline
    $t^*_1$ & 99.34 &  0.0015 \\
    $t^*_2$ & 99.65 &  0.00040 \\
    $t^*_3$ & 98.98 &  0.0015 \\
    $t^*_4$ & 99.30 &  0.00093 \\
    $t^*_5$ & 99.73 &  0.000094 \\
    $t^*_6$ & 98.31 &  0.0026
  \end{tabular}
  \caption{Mean values for the detection accuracies shown in \fig{fig:accuracies}.}
  \label{table:accuracies}
\end{table}

@@

This syllable detector is appropriate for zebra finch song, and
although our tests were carried out on songs from that species, it is
also likely to work well for Bengalese finches due to their similarly stereotyped syllables.  It offers the
following benefits:
\begin{itemize}
\item The detector is accurate. False negative and false positive
  rates can be well under 1\% and 0.001\% respectively, and trading
  these two numbers off against each other is through a single
  relative-cost parameter.
\item Latency is generally under a millisecond, with jitter around 2
  ms.
\item Works on a wide range of target syllables using the default
  values described here, generally eliminating the need for
  hand-tuning.
\item Runs fast enough for syllable-modification experiments on
  inexpensive consumer-grade hardware, although we recommend that the
  training phase be run on a fast desktop system with 32 GB of RAM.
\item A single detector can generate different target pulses for
  multiple syllables at almost no additional computational cost during
  runtime, although training time will increase.
\end{itemize}
